---
title: "R Project 1 - Hello R"
author: "Regis Ouedraogo"
date: "1/23/2020"
output: 
  html_document: 
    fig_height: 6
    fig_width: 8
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

The datasaurus_dozen file have a data frame with 1846 rows and 3 columns.
The variables included in the data frame are :
dataset , 
x (x values) , 
y (y values)



### Exercise 2


dino_data <- datasaurus_dozen %>%

 filter(dataset == "dino")
 
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +

  geom_point()


dino_data %>%
  summarize(r = cor(x, y))


### Exercise 3

star_data <- datasaurus_dozen %>%

filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) +

geom_point()

ggplot(data = star_data, mapping = aes(x = x, y = y)) +

geom_point()

star_data %>%

summarize(r = cor(x, y))


```{r plot-star}
```

 this value compared to the r of dino is almost the same 
 dino= 0.0645
 star= 0.0630
```{r cor-star}
```

### Exercise 4

circle_data <- datasaurus_dozen %>%

    filter(dataset == "circle")
    
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +

    geom_point()
    
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +

    geom_point()
    
circle_data %>%

    summarize(r = cor(x, y))

```{r}
```
 this value compared to the r of dino is almost the same 
 dino = 0.0645
 circle = 0.0683
```{r}
```

### Exercise 5


ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+

geom_point()+

facet_wrap(~ dataset, ncol = 3) + # facet the dataset variable, in 3 cols

theme(legend.position = "none")

datasaurus_dozen %>%

group_by(dataset) %>%

summarize(r = cor(x, y)) %>%

print(13)
