---
title: "R Project 1 - Hello R"
author: "Regis Ouedraogo"
date: "1/23/2020"
output: html_document
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

The datasaurus_dozen file have a data frame with 1846 rows and 3 columns.
The variables included in the data frame are :
dataset , 
x (x values) , 
y (y values)



### Exercise 2


dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()


dino_data %>%
  summarize(r = cor(x, y))


### Exercise 3

dino_data <- datasaurus_dozen %>%
filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
geom_point()
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
geom_point()
dino_data %>%
summarize(r = cor(x, y))


```{r plot-star}
```

 this value compared to the r of dino is almost the same 
 dino= 0.0645
 star= 0.0630
```{r cor-star}
```

### Exercise 4

(Add code and narrative as needed. Note that two R chunks are given but they are not labeled. Use the convention from above to name them appropriately.)

```{r}
```

```{r}
```

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, green C+.)